Graph Generators for Data Science: A Survey

### 2018-06-28 generators_LinkedData.tex
Sherif Changes

\subsection{Semantic Web}
\label{sec:generators_LinkedData}
With the dawn of the concept of Linked Data there have naturally emerged also respective benchmarks involving both real-world data sets and synthetic data sets with real-world characteristics. The used data sets correspond to RDF representation of relational-like data~\cite{Guo2005158,Bizer09theberlin}, social network-like data~\cite{Schmidt2010}, or specific and significantly more complex data structures such as biological data~\cite{Wu2014}. In the following overview we focus on benchmarking systems involving a kind of data generator or data modifier. Other types of systems or particular results can be found, e.g., at~\cite{RdfStoreBenchmarking}.

Considering the Big Data world, the Linked Data in general definitely belong to this group since we assume that the Linked (Open) Data Sets form a common Linked Open Data cloud\footnote{\url{http://lod-cloud.net/}}. On the other hand, the particular data sets can be relatively small.

\paragraph{LUBM} The use-case driven Lehigh University Benchmark (LUBM)\footnote{\url{http://swat.cse.lehigh.edu/projects/lubm/}} considers the university domain. The ontology defines 43 classes and 32 properties, including 25 object properties and 7 datatype properties~\cite{Guo2005158}. The LUBM benchmark also provides 14 test queries. The authors focus on \emph{extensional} queries, i.e., queries about the instance data over ontologies, as an opposite to \emph{intentional} queries (i.e., queries about classes and properties). The Univ-Bench Artificial  (UBA) data generator features random and repeatable data generation (exploting classical linear congruential generator, LCG, of numbers). In particular, data generated by the tool are exactly repeatable with respect to universities (assigning them zero-based indexes, i.e., the first university is named University0 and so on).  The generator allows a user to specify the seed for random number generation, the number of universities, and the starting index of the universities.

An extension of LUBM, the Lehigh BibTeX Benchmark (LBBM)~\cite{Wang2005}, enables generating synthetic data for different ontologies. The generation is divided into two phases: (1) the property-discovering phase, and (2) the data generation phase. The authors present a probabilistic model that, given representative data of some domain, can capture the properties of the data and generate synthetic data that has similar properties. A Monte Carlo algorithm is used to generate synthetic data. The approach is demonstrated on the Lehigh University BibTeX ontology which consists of 28 classes and 80 properties. 12 test queries were designed for  the benchmark data. Another extension of LUBM, the University Ontology Benchmark (UOBM)\footnote{\url{https://www.cs.ox.ac.uk/isg/tools/UOBMGenerator/}}, focuses on two aspects: (1) usage of all constructs of OWL Lite and OWL DL~\cite{owl} and (2) lack of necessary links between the generated data which thus form isolated graphs~\cite{Ma:2006:TCO:2094613.2094629}. In the former case the original ontology is replaced by the two types of extended versions from which the user can choose. In the latter case cross-university and cross-department links are added to create a more complex graph.

@@

\paragraph{SIB} The authors of the Social Network Intelligence BenchMark (SIB)\footnote{\url{https://www.w3.org/wiki/Social_Network_Intelligence_BenchMark}} claim that current benchmarks are limited in representing the real RDF datasets and are mostly relational-like. Hence, they propose a benchmark for challenging query processing over real graphs~\cite{sib}. It simulates an RDF backend of a social network site, in which users and their interactions form an social graph of social activities such as writing posts, posting comments, creating/managing groups, etc. The distribution of generated data on each relation conforms to the data distribution analyzed over real-world social networks. Association rules are included in order to convey the real-world data correlation into synthetic data. The  generated data is linked with the RDF datasets from DBpedia. The benchmark specification contains 3 query mixes -- interactive, update, and analysis -- expressed in SPARQL 1.1 Working Draft.

\paragraph{Geographica} The Geographica benchmark \footnote{\url{http://geographica.di.uoa.gr/}} has been designed target the area of geospatial data~\cite{DBLP:conf/semweb/GarbisKK13} and respective SPARQL extensions GeoSPARQL~\cite{battle2012enabling} and stSPARQL~\cite{koubarakis2010modeling}. The benchmark involves (1) a real-world workload based on publicly available linked data sets covering a range of geometry types (e.g., points, lines, polygons) and (2) a synthetic workload. In the former case they further distinguish (1) a micro benchmark that tests primitive spatial functions (involving 29 queries) and (2) macro benchmark that tests the performance of RDF stores in typical application scenarios like reverse geocoding or map search and browsing (consisting of 11 queries). In the latter case of a synthetic workload the generator produces synthetic datasets of various sizes that corresponds to an ontology based on OpenStreetMap (i.e., states in a country, land ownership, roads and  points of interest) and instantiates query templates. The spatial extent of the land ownership dataset constitutes a uniform grid of $n \times n$ hexagons, whereas the size of each dataset is given relatively to $n$. The synthetic workload generator produces SPARQL queries corresponding to spatial selection and spatial joins by instantiating 2 query templates.

@@

\paragraph{RBench} RBench~\cite{Qiao:2015:RAR:2723372.2746479} is an application-specific benchmark which takes any RDF dataset as a template, and generates a set of synthetic datasets with similar characteristic, the required size scaling factor $s$ and the (node) degree scaling factor $d$. A generated benchmark dataset is considered similar to the given dataset if their values for the dataset evaluation metrics and query evaluation times for different techniques are similar. Three evaluation metrics -- dataset coherence (i.e., a measure how uniformly predicates are distributed among the same type/class), relationship specialty (i.e., the number of occurrences of the same predicate associated with each resource), and literal diversity -- are utilized for this purpose. A query generation process is proposed to generate 5 types of queries (node queries, edge queries, star queries, path queries, and subgraph queries) for any generated data. The benchmark project FEASIBLE~\cite{Saleem2015} is also an application-specific benchmark; however, contrary to RBench, it is able to generate benchmarks from a set of queries (in particular from query logs) by selecting prototypical queries of a user-defined
size from the input set of queries.

\paragraph{LDBC}  The Linked Data Benchmark Council\footnote{\url{http://ldbcouncil.org/industry/organization/origins}} (LDBC)~\cite{Angles:2014:LDB:2627692.2627697} is a result of a (closed) EU project that brought together a community of academic researchers and industry, whose main objective was the development of open source, yet industrial grade, benchmarks for graph and RDF databases. The following three benchmarks were developed and are currently maintained.

The Semantic Publishing Benchmark (SPB)~\cite{spb} is inspired by the Media/Publishing industry (namely BBC\footnote{\url{http://www.bbc.com/}}). The application scenario considers a media or a publishing organization that deals with large volume of streaming content, namely news, articles or  ``media assets''. This content is enriched with metadata that describes it and links it to reference knowledge -- taxonomies and databases that include relevant concepts, entities and factual information. The SPB data generator produces scalable in size synthetic large data. Synthetic data consists of a large number of annotations of media assets that refer entities found in reference datasets. The data generator models three types of relations in produced synthetic data: (1) clustering of data, (2) correlations of entities, and (3) random tagging of entities. Two workloads are provided: (1) basic, involving an interactive query-mix, querying the relations between entities in reference data, and (2) advanced,  consisting of interactive and analytical query-mixes.

The Social Network Benchmark (SNB) models a social network akin to Facebook (see Section~\ref{sec:generators_socialnetworks}).

Graphalytics~\cite{Iosup:2016:LGB:3007263.3007270} is an industrial-grade benchmark for graph analysis platforms. It involves 6 real-world datasets and 2 synthetic datasets generated by LDBC SNB (see Section~\ref{}) and Graph500 (see Section~\ref{}). The benchmark involves 6 algorithms: breadth-first search, PageRank, weakly connected components, community detection using label propagation, local clustering coefficient, and single-source shortest paths.

LinkGen~\cite{10.1007/978-3-319-46547-0_12}

>>>>

\subsection{Semantic Web}
\label{sec:generators_LinkedData}
With the dawn of the concept of Linked Data there have naturally emerged also respective benchmarks involving both real-world data sets and synthetic data sets with real-world characteristics. The used data sets correspond to RDF representation of relational-like data~\cite{Guo2005158,Bizer09theberlin}, social network-like data~\cite{Schmidt2010}, or specific and significantly more complex data structures such as biological data~\cite{Wu2014}. In this section, we provide an overview of benchmarking systems involving a kind of graph-based RDF data generator or data modifier. %Other types of systems or particular results can be found, e.g., at~\cite{RdfStoreBenchmarking}.

\iffalse
Considering the Big Data world, the Linked Data in general definitely belong to this group since we assume that the Linked (Open) Data Sets form a common Linked Open Data cloud\footnote{\url{http://lod-cloud.net/}}. On the other hand, the particular data sets can be relatively small.
\fi

\paragraph{LUBM} The use-case driven Lehigh University Benchmark (LUBM)\footnote{\url{http://swat.cse.lehigh.edu/projects/lubm/}} considers the university domain. The ontology defines 43 classes and 32 properties, including 25 object properties and 7 datatype properties~\cite{Guo2005158}. The \texttt{LUBM} benchmark also provides 14 test queries. The authors focus on \emph{extensional} queries, i.e., queries about the instance data over ontologies, as an opposite to \emph{intentional} queries (i.e., queries about classes and properties). The Univ-Bench Artificial  (UBA) data generator features random and repeatable data generation (exploting classical linear congruential generator, LCG, of numbers). In particular, data generated by the tool are exactly repeatable with respect to universities (assigning them zero-based indexes, i.e., the first university is named University0 and so on).  The generator allows a user to specify the seed for random number generation, the number of universities, and the starting index of the universities.

An extension of \texttt{LUBM}, the Lehigh BibTeX Benchmark (LBBM)~\cite{Wang2005}, enables generating synthetic data for different ontologies. The generation is divided into two phases: (1) the property-discovering phase, and (2) the data generation phase. The authors present a probabilistic model that, given representative data of some domain, can capture the properties of the data and generate synthetic data that has similar properties. A Monte Carlo algorithm is used to generate synthetic data. The approach is demonstrated on the Lehigh University BibTeX ontology which consists of 28 classes and 80 properties. 12 test queries were designed for  the benchmark data. Another extension of LUBM, the University Ontology Benchmark (UOBM)\footnote{\url{https://www.cs.ox.ac.uk/isg/tools/UOBMGenerator/}}, focuses on two aspects: (1) usage of all constructs of OWL Lite and OWL DL~\cite{owl} and (2) lack of necessary links between the generated data which thus form isolated graphs~\cite{Ma:2006:TCO:2094613.2094629}. In the former case the original ontology is replaced by the two types of extended versions from which the user can choose. In the latter case cross-university and cross-department links are added to create a more complex graph.

@@

\paragraph{SIB} The developers of the Social Network Intelligence BenchMark (SIB)\footnote{\url{https://www.w3.org/wiki/Social_Network_Intelligence_BenchMark}} based the design of their benchmark based on the claim that existing benchmarks are limited in representing the real RDF datasets and are mostly relational-like. Hence, they propose a benchmark for challenging query processing over real graphs~\cite{sib}. It simulates an RDF backend of a social network site, in which users and their interactions form an social graph of social activities such as writing posts, posting comments, creating/managing groups, etc. The distribution of generated data on each relation conforms to the data distribution analyzed over real-world social networks. Association rules are included in order to convey the real-world data correlation into synthetic data. The  generated data is linked with the RDF datasets from DBpedia. The benchmark specification contains 3 query mixes -- interactive, update, and analysis -- expressed in SPARQL 1.1 Working Draft.

\paragraph{Geographica} The Geographica benchmark \footnote{\url{http://geographica.di.uoa.gr/}} has been designed target the area of geospatial data~\cite{DBLP:conf/semweb/GarbisKK13} and respective SPARQL extensions \texttt{GeoSPARQL}~\cite{battle2012enabling} and \texttt{stSPARQL}~\cite{koubarakis2010modeling}. The benchmark involves (1) a real-world workload based on publicly available linked data sets covering a range of geometry types (e.g., points, lines, polygons) and (2) a synthetic workload. In the former case they further distinguish (1) a micro benchmark that tests primitive spatial functions (involving 29 queries) and (2) macro benchmark that tests the performance of RDF stores in typical application scenarios like reverse geocoding or map search and browsing (consisting of 11 queries). In the latter case of a synthetic workload the generator produces synthetic datasets of various sizes that corresponds to an ontology based on OpenStreetMap (i.e., states in a country, land ownership, roads and  points of interest) and instantiates query templates. The spatial extent of the land ownership dataset constitutes a uniform grid of $n \times n$ hexagons, whereas the size of each dataset is given relatively to $n$. The synthetic workload generator produces SPARQL queries corresponding to spatial selection and spatial joins by instantiating 2 query templates.

@@

\paragraph{RBench} RBench~\cite{Qiao:2015:RAR:2723372.2746479} is an application-specific benchmark which takes any RDF dataset as a template, and generates a set of synthetic datasets with similar characteristic, the required size scaling factor $s$ and the (node) degree scaling factor $d$. A generated benchmark dataset is considered similar to the given dataset if their values for the dataset evaluation metrics and query evaluation times for different techniques are similar. Three evaluation metrics -- dataset coherence (i.e., a measure how uniformly predicates are distributed among the same type/class), relationship specialty (i.e., the number of occurrences of the same predicate associated with each resource), and literal diversity -- are utilized for this purpose. A query generation process is proposed to generate 5 types of queries (node queries, edge queries, star queries, path queries, and subgraph queries) for any generated data. The benchmark project \texttt{FEASIBLE}~\cite{Saleem2015} is also an application-specific benchmark; however, contrary to RBench, it is able to generate benchmarks from a set of queries (in particular from query logs) by selecting prototypical queries of a user-defined
size from the input set of queries.

\paragraph{LDBC}  The Linked Data Benchmark Council\footnote{\url{http://ldbcouncil.org/industry/organization/origins}} (LDBC)~\cite{Angles:2014:LDB:2627692.2627697} is a result of a (closed) EU project that brought together a community of academic researchers and industry that had the main objective of developing an open source, yet industrial grade, benchmarks for graph and RDF databases. \iffalse The following three benchmarks were developed and are currently maintained.\fi In the Semantic Web domain, the project released the Semantic Publishing Benchmark (SPB)~\cite{spb} that has been inspired by the Media/Publishing industry (namely BBC\footnote{\url{http://www.bbc.com/}}). The application scenario of this benchmark considers a media or a publishing organization that deals with large volume of streaming content, namely news, articles or  ``media assets''. This content is enriched with metadata that describes it and links it to reference knowledge -- taxonomies and databases that include relevant concepts, entities and factual information. The SPB data generator produces scalable in size synthetic large data. Synthetic data consists of a large number of annotations of media assets that refer entities found in reference datasets. The data generator models three types of relations in produced synthetic data: (1) clustering of data, (2) correlations of entities, and (3) random tagging of entities. Two workloads are provided: (1) basic, involving an interactive query-mix, querying the relations between entities in reference data, and (2) advanced,  consisting of interactive and analytical query-mixes. The LDBC designed two other benchmarks: the Social Network Benchmark (SNB)~\cite{Erling:2015:LSN:2723372.2742786} for the social network domain  (see Section~\ref{sec:generators_socialnetworks}) and Graphalytics~\cite{Iosup:2016:LGB:3007263.3007270}   for the analytics domain (see Section~\ref{sec:generators_analytics}).

\paragraph{LinkGen} LinkGen is a synthetic linked data generator that has been designed to generate RDF datasets for a given vocabulary~\cite{10.1007/978-3-319-46547-0_12}. The generator is designed to receive a vocabulary as an input  and supports two statistical distribution techniques for generating entities: Gaussian distribution and Zipf's power-law distribution. \texttt{LinkGen} can augment the generated data with inconsistent and noisy  data such as writing two conflicting values for a given datatype property,  adding triples with syntactic errors, adding wrong statement by assigning invalid domain and creating instances with no type information. The generator is also designed with  an option to inter-link the generated instances with real ones given that the user provides entities from real datasets. The datasets can be generated in any of of two modes: on-disk and streaming.

### 2018-06-28 generators_SocialNetworks.tex
Sherif Changes

On-line social networks, like Facebook, Twitter, or LinkedIn, have become a
phenomenon used by billions of people every day and thus providing extremely
useful information for various domains. However, an analysis of such type of
graph has to cope with two problems: (1) availability of the data and (2)
privacy of the data. Hence, data generators which provide realistic synthetic
social network graphs are in great demand.

Analyses of social networks identify their various specific
features~\cite{Chakrabarti:2006:GML:1132952.1132954}. For example, the social
graph has high \emph{clustering coefficient}, i.e. the degree of transitivity of
a graph. Or, its diameter, i.e. the minimum number of hops in which some
fraction (e.g., 90\%) of all connected pairs of nodes can reach each other, is
usually low due to weak ties joining faraway cliques. Another important aspect
of social networks is the community effect. A detailed study of structure of
communities in 70 real-world networks is provided, e.g., in
paper~\cite{Leskovec:2008:SPC:1367497.1367591}. Authors of
paper~\cite{Prat-Perez:2014:CSS:2621934.2621942} analyze the structure of
communities (clustering coefficient, triangle participation ratio, bridges,
diameter, conductance and size) in both real graphs and output by existing graph
generators LFR~\cite{PhysRevE.78.046110} and the
LDBC-SNB~\cite{Erling:2015:LSN:2723372.2742786}. %They discover that communities
found among different graphs follow quite similar distributions and that
communities in a single graph have diverse nature, and are difficult to fit with
a single model.

@@

\paragraph{Realistic Social Network}
Paper~\cite{Barrett:2009:GAL:1995456.1995598} focuses on construction of
realistic social networks using a combination of public and private data sets
and large-scale agent based techniques. The process works as follows: Step 1
creates a synthetic population by integrating databases from commercial and
public sources. In Step 2, a set of activity templates are determined. Each
synthetic individual is assigned a 24-hour activity sequence including
geo-locations for each activity.

To demonstrate the approach, the authors develop a synthetic population for the
United States that models every individual in the population. The synthetic
population is a set of geographically located people and households. Household
structure and demographics are derived from U.S. Census data. The activity
templates are  based on several thousand responses to an activity or time-use
survey. Demographic information for each person and location, a minute-by-minute
schedule of each person's activities, and the locations where these activities
take place is generated by a combination of simulation and data fusion
techniques. This information is captured by a dynamic social contact network.

Similar agent-based strategies can be found, e.g., in papers~\cite{Bernstein:2013:SAS:2499604.2499609}.

\paragraph{Linkage vs. Activity Graphs} Paper~\cite{Yao2011} distinguishes two
types of social network graphs -- the \emph{linkage graph}, where nodes stand
for the people in the social network and edges are their friendship links, and
the \emph{activity graph}, where nodes also stand for the people but edges stand
for their interactions. On the basis of analysis of
Flickr\footnote{\url{https://www.flickr.com/}} social links and
Epinions\footnote{\url{http://www.epinions.com/}} network of user interactions,
the authors discover that they both exhibit power-law degree distribution, high
clustering coefficient (community structure), and small diameter; also regarding
the dynamic properties they both follow densification law and relatively stable
clustering coefficient over time. However, the authors do not observe diameter
shrinking in Epinions? activity graph and there is a difference in degree
correlation (how frequently nodes with similar degrees connect to each other).
Namely linkage graphs have positive degree correlation whereas activity graphs
show neutral degree correlation.

With regards to the findings, the proposed generator focusses on linkage graphs
with positive degree correlation. For this purpose it extends the ``forest
fire'' spreading process algorithm~\cite{Leskovec:2005:GOT:1081870.1081893} with
link symmetry. It has two parameters -- the \emph{burning probability} $P_b$
which is in charge of the burning process, and the \emph{symmetry probability}
$P_s$ which indicates backward linking from old nodes to new ones. $P_b$
controls a BFS-based forward burning process. The fire burns increasingly
fiercely with $P_b$ approaching 1. Meanwhile, $P_s$ adds fuel to the fire as it
brings more links. It gives chances for big nodes to connect back to big nodes.

\paragraph{LinkBench} The LinkBench
benchmark~\cite{Armstrong:2013:LDB:2463676.2465296} aims to predict the
performance of a database when used for persistent storage of Facebook?s
production data. The benchmark considers true Big Data and related problems with
sharding, replication etc. The social graph at Facebook comprises objects (nodes
with IDs, version, timestamp and data) and associations (directed edges, pairs
of node IDs, with visibility, timestamp and data). The size of the target graph
is the number of nodes. Graph edges are generated concurrently with graph nodes
during bulk loading. The node ID space is divided into chunks based on the ID of
the source node which  are processed in parallel. The edges of the graph are
generated in accordance with the results of analysis of real-world Facebook data
(such as outdegree distribution). A workload corresponding to 10 graph
operations (such as insert object, count the number of associations etc.) and
their respective characteristics over the real-world data is generated for the
synthetic data.

\paragraph{S3G2} The Scalable Structure-correlated Social Graph Generator
(S3G2)~\cite{Pham2013} is a general framework which  generates a directed
labeled graph, where the nodes are objects with property values, and their
structure is determined by the class a node belongs to. S3G2 does not aim at
generating near real-world data, but at generating synthetic graphs which a
correlated structure. It causes that the probability to choose a certain
property value (from a pre-defined dictionary), or the probability to connect
two nodes with an edge are influenced by existing data values. For example, it
is possible to have a correlated degree distribution, from which the degree of
each node is generated, correlated with properties of node. Hence the generator
can ensure that, e.g., people with many friends in a social network will
typically post more pictures than people with few friends, i.e., the amount of
friend nodes influences the amount of posted comment and picture nodes.

The data generation process starts with generating a number of nodes with
property values generated according to specified property value correlations and
then adding respective edges according to specified correlation dimensions. It
has multiple phases, each focusing on one correlation dimension. Each pass along
one correlation dimension is a Map phase in which data is generated, followed by
a Reduce phase that sorts the data along the correlation dimension in the next
pass. A heuristic observation that ``the probability that two nodes are
connected is typically skewed with respect to some similarity between the
nodes'' enables to focus only on sliding window of most probable candidates.

The core idea of the framework is demonstrated using an example of a social
network (consisting of persons and social activities).  The dictionaries for
property values are inspired by DBpedia and provided with 20 property value
correlations. The edges are generated according to 3 correlation dimensions.

@@

Attribute Synthetic Generator (ASG) is a network generator for reproducing the
node feature distribution of standard networks and rewiring the network to
preferentially connect nodes that exhibit a high feature similarity. The network
is initialized with a group of three nodes, and new nodes and links are added to
the network based on link density, homophily, and feature similarity. As new
nodes are created, their labels are assigned based on the prior label
distribution. After the network has reached the same number of nodes as the
original social media dataset, each node initially receives a random attribute
assignment. Then a stochastic optimization process is used to move the initial
assignments closer to the target distribution extracted from social media
dataset using the Particle Swarm Optimization algorithm. The tuned attributes
are then used to add additional links to the network based on the feature
similarity parameter -- a source node is selected randomly and connected to the
most similar node.

Multi-Link Generator (MLG) further  uses link co-occurrence statistics from the
original dataset to create a multiplex network. MLG uses the same network growth
process as ASG.. Based on the link density parameter, either a new node is
generated with a label based on the label distribution of the target dataset or
a new link is created between two existing nodes.

@@

The generated data have become a part if several graph benchmarks, such as
GraphBIG~\cite{Nai:2015:GUG:2807591.2807626}.

\paragraph{Towards More Realistic Data} The authors of
paper~\cite{Nettleton2016} claim that the main body of existing work lies in
topology generation which approximate the characteristics of a real social
network (such as a small graph diameter, small average path length, skew degree
distribution, and community structures), however without data. Hence, they
implement a general stochastic modeling system which allows the users to
populate a graph topology with data. The approach has three steps: (1) topology
generation (using R-MAT) plus community identification using the Louvain
method~\cite{1742-5468-2008-10-P10008} or usage of a real-world topology from
SNAP\footnote{\url{https://snap.stanford.edu/data/}}, (2) data definition
(following distribution profiles, attribute value definitions, using a
parameterizable set of data propagation rules and affinities), and (3) data
population.

>>>>

On-line social networks, like Facebook, Twitter, or LinkedIn, have become a
phenomenon used by billions of people every day and thus providing extremely
useful information for various domains. However, an analysis of such type of
graph has to cope with two problems: (1) availability of the data and (2)
privacy of the data. Hence, data generators which provide realistic synthetic
social network graphs are in great demand. In general, analyses of social networks identify their various specific
features~\cite{Chakrabarti:2006:GML:1132952.1132954}. For example, the social
graph has high \emph{clustering coefficient}, i.e. the degree of transitivity of
a graph. Or, its diameter, i.e. the minimum number of hops in which some
fraction (e.g., 90\%) of all connected pairs of nodes can reach each other, is
usually low due to weak ties joining faraway cliques. Another important aspect
of social networks is the community effect. A detailed study of structure of
communities in 70 real-world networks is provided, e.g., in
paper~\cite{Leskovec:2008:SPC:1367497.1367591}. Authors of
paper~\cite{Prat-Perez:2014:CSS:2621934.2621942} analyze the structure of
communities (clustering coefficient, triangle participation ratio, bridges,
diameter, conductance and size) in both real graphs and output by existing graph
generators LFR~\cite{PhysRevE.78.046110} and the
LDBC-SNB~\cite{Erling:2015:LSN:2723372.2742786}. %They discover that communities
found among different graphs follow quite similar distributions and that
communities in a single graph have diverse nature, and are difficult to fit with
a single model.

@@

\paragraph{Realistic Social Network}
~\cite{Barrett:2009:GAL:1995456.1995598} focused on construction of
realistic social networks using a combination of public and private data sets
and large-scale agent based techniques. The process works as follows: Step 1
creates a synthetic population by integrating databases from commercial and
public sources. In Step 2, a set of activity templates are determined. Each
synthetic individual is assigned a 24-hour activity sequence including
geo-locations for each activity. To demonstrate the approach, the authors develop a synthetic population for the
United States that models every individual in the population. The synthetic
population is a set of geographically located people and households. Household
structure and demographics are derived from U.S. Census data. The activity
templates are  based on several thousand responses to an activity or time-use
survey. Demographic information for each person and location, a minute-by-minute
schedule of each person's activities, and the locations where these activities
take place is generated by a combination of simulation and data fusion
techniques. This information is captured by a dynamic social contact network. Similar methods for agent-based strategies have been reported in~\cite{Bernstein:2013:SAS:2499604.2499609}.

\paragraph{Linkage vs. Activity Graphs} ~\cite{Yao2011} distinguished between two
types of social network graphs -- the \emph{linkage graph}, where nodes stand
for the people in the social network and edges are their friendship links, and
the \emph{activity graph}, where nodes also stand for the people but edges stand
for their interactions. On the basis of analysis of
Flickr\footnote{\url{https://www.flickr.com/}} social links and
Epinions\footnote{\url{http://www.epinions.com/}} network of user interactions,
the authors discover that they both exhibit power-law degree distribution, high
clustering coefficient (community structure), and small diameter; also regarding
the dynamic properties they both follow densification law and relatively stable
clustering coefficient over time. However, the authors do not observe diameter
shrinking in Epinions? activity graph and there is a difference in degree
correlation (how frequently nodes with similar degrees connect to each other).
Namely linkage graphs have positive degree correlation whereas activity graphs
show neutral degree correlation. With regards to the findings, the proposed generator focusses on linkage graphs
with positive degree correlation. For this purpose it extends the ``forest
fire'' spreading process algorithm~\cite{Leskovec:2005:GOT:1081870.1081893} with
link symmetry. It has two parameters -- the \emph{burning probability} $P_b$
which is in charge of the burning process, and the \emph{symmetry probability}
$P_s$ which indicates backward linking from old nodes to new ones. $P_b$
controls a BFS-based forward burning process. The fire burns increasingly
fiercely with $P_b$ approaching 1. Meanwhile, $P_s$ adds fuel to the fire as it
brings more links. It gives chances for big nodes to connect back to big nodes.

\paragraph{LinkBench} The LinkBench
benchmark~\cite{Armstrong:2013:LDB:2463676.2465296} has been designed to predict the
performance of a database when used for persistent storage of Facebook's
production data. The benchmark considers true Big Data and related problems with
sharding, replication etc. The social graph at Facebook comprises objects (nodes
with IDs, version, timestamp and data) and associations (directed edges, pairs
of node IDs, with visibility, timestamp and data). The size of the target graph
is the number of nodes. Graph edges are generated concurrently with graph nodes
during bulk loading. The node ID space is divided into chunks based on the ID of
the source node which  are processed in parallel. The edges of the graph are
generated in accordance with the results of analysis of real-world Facebook data
(such as outdegree distribution). A workload corresponding to 10 graph
operations (such as insert object, count the number of associations etc.) and
their respective characteristics over the real-world data is generated for the
synthetic data.

\paragraph{S3G2} The Scalable Structure-correlated Social Graph Generator
(S3G2)~\cite{Pham2013} is a general framework which  generates a directed
labeled graph, where the nodes are objects with property values, and their
structure is determined by the class a node belongs to. S3G2 does not aim at
generating near real-world data, but at generating synthetic graphs which a
correlated structure. It causes that the probability to choose a certain
property value (from a pre-defined dictionary), or the probability to connect
two nodes with an edge are influenced by existing data values. For example, it
is possible to have a correlated degree distribution, from which the degree of
each node is generated, correlated with properties of node. Hence the generator
can ensure that, e.g., people with many friends in a social network will
typically post more pictures than people with few friends, i.e., the amount of
friend nodes influences the amount of posted comment and picture nodes. The data generation process starts with generating a number of nodes with
property values generated according to specified property value correlations and
then adding respective edges according to specified correlation dimensions. It
has multiple phases, each focusing on one correlation dimension. Each pass along
one correlation dimension is a Map phase in which data is generated, followed by
a Reduce phase that sorts the data along the correlation dimension in the next
pass. A heuristic observation that ``the probability that two nodes are
connected is typically skewed with respect to some similarity between the
nodes'' enables to focus only on sliding window of most probable candidates. The core idea of the framework is demonstrated using an example of a social
network (consisting of persons and social activities).  The dictionaries for
property values are inspired by DBpedia and provided with 20 property value
correlations. The edges are generated according to 3 correlation dimensions.

@@

Attribute Synthetic Generator (ASG) is a network generator for reproducing the
node feature distribution of standard networks and rewiring the network to
preferentially connect nodes that exhibit a high feature similarity. The network
is initialized with a group of three nodes, and new nodes and links are added to
the network based on link density, homophily, and feature similarity. As new
nodes are created, their labels are assigned based on the prior label
distribution. After the network has reached the same number of nodes as the
original social media dataset, each node initially receives a random attribute
assignment. Then a stochastic optimization process is used to move the initial
assignments closer to the target distribution extracted from social media
dataset using the Particle Swarm Optimization algorithm. The tuned attributes
are then used to add additional links to the network based on the feature
similarity parameter -- a source node is selected randomly and connected to the
most similar node. Multi-Link Generator (MLG) further  uses link co-occurrence statistics from the
original dataset to create a multiplex network. MLG uses the same network growth
process as ASG.. Based on the link density parameter, either a new node is
generated with a label based on the label distribution of the target dataset or
a new link is created between two existing nodes.

@@

%The generated data have become a part if several graph benchmarks, such as GraphBIG~\cite{Nai:2015:GUG:2807591.2807626}.

\paragraph{Towards More Realistic Data} ~\cite{Nettleton2016} argued that the main body of existing work lies in
topology generation which approximate the characteristics of a real social
network (such as a small graph diameter, small average path length, skew degree
distribution, and community structures), however without data. Hence, they
introduced a general stochastic modeling system which allows the users to
populate a graph topology with data. The approach has three steps: (1) topology
generation (using R-MAT) plus community identification using the Louvain
method~\cite{1742-5468-2008-10-P10008} or usage of a real-world topology from
SNAP\footnote{\url{https://snap.stanford.edu/data/}}, (2) data definition
(following distribution profiles, attribute value definitions, using a
parameterizable set of data propagation rules and affinities), and (3) data
population.
